Equivalence Testing and the Second Generation P-Value

### 2018-07-19 sgpv_vs_TOST.Rmd
add link to Rmd

source("TOST_to_SGPV.R")
```

@@

As a descriptive statistic it is somewhat limited. SGPV is 1 for a range of values (see Figure 1) where the *p*-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1). Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65). Since the SGPV is always directly related to a *p*-value from the TOST procedure, different SGPV can be interpreted in the same manner as different *p*-values. From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range. From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis while controlling our error rate at a known maximum.

>>>>

source("TOST_to_SGPV.R")
```
The RMarkdown file with the reproducible code of this text is [here](https://github.com/Lakens/TOST_vs_SGPV/blob/master/sgpv_vs_TOST.Rmd).

@@

As a descriptive statistic it is somewhat limited. SGPV is 1 for a range of values (see Figure 1) where the *p*-values for the TOST procedure range differ (e.g., different equivalence tests with *p* = 0.049 and *p* = 0.0001 have a SGPV of 1). Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65). Since the SGPV is always directly related to a *p*-value from the TOST procedure, different SGPV can be interpreted in the same manner as different *p*-values. From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range. From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis is true while controlling our error rate at a known maximum.
